---
output: github_document
---

# __tRiviascoRe__: a package to score teams during the useR2021 tRivia event

To install and load the package use:

```{r install, eval=F}
remotes::install_github("saramortara/tRiviascoRe")
library(tRiviascoRe)
```

```{r load-dev, echo=F, message=FALSE}
devtools::load_all()
```


```{r libs, message=FALSE}
library(tidyr)
library(dplyr)
library(readr)
library(gsheet)
```

## What do you need?

1. A Google form with multiple choice questions. All questions must have unique names

2. A reference data frame with two or three columns: `question_name`, `correct_answer` and `round` (optional)

3. The answers from the google form

## How we run the code


####  Reference table 

```{r}
ref_url <- "https://docs.google.com/spreadsheets/d/1uCPz4XFWUGd20-fVgXjIo59eWp31AREzTlXCuEN8Vn0/edit#gid=0"
ref <- read_csv(construct_download_url(ref_url))

# Score points vector
score <- c(2, 3, 5, 10)
```


### Round 1

```{r round1}

url1 <- "https://docs.google.com/spreadsheets/d/1JqthtHHCFat1NdUUzM-9kyS-Vi789GFHywPu0eJ_5UE/edit#gid=1753062260"

r1 <- read_csv(construct_download_url(url1))

res1 <- score_trivia(r1, n_round = 1, score = score[1], ref)

res1
```

### Round 2


```{r round2}

url2 <- "https://docs.google.com/spreadsheets/d/1H3V2DpZHbtY-TtOmyTVLWJXUEiPgMVdDisJGTQ2deB4/edit#gid=464947112"

r2 <- read_csv(construct_download_url(url2))

res2 <- score_trivia(r2, n_round = 2, score = score[2], ref)

res2
```


### Round 3

```{r round3}

url3 <- "https://docs.google.com/spreadsheets/d/1blvK5r3WGHQbatNeqFt3H0nIVXPXYpaS_CYY6IiMRsU/edit?usp=sharing"

r3 <- read_csv(construct_download_url(url3))


res3 <- score_trivia(r3, n_round = 3, score = score[3], ref)

res3

```


### Round 4 

```{r}
url4 <- "https://docs.google.com/spreadsheets/d/1FavTAbTzBqDXnBJTIjeKMY8bhLzUF8Kx9NSIgMczCuI/edit?usp=sharing"

r4 <- read_csv(construct_download_url(url4))

res4 <- score_trivia(r4, n_round = 4, score = score[4], ref)

res4
```


### Final Score ------------------------------------------------------------------

```{r final}

score_list <- list(res1, res2, res3, res4)

res <- bind_rows(score_list)

rank_teams(res)
```

